Hydra Battles in Coq

### 2020-11-23 doc/chapter-powers.tex
Representation of Euclidean chains as lists of instructions. works, but still to simplify and document the proofs.

Please define an Euclidean chain generator using this data structure, and prove its correctness (partially done  in ~\href{../theories/html/hydras.additions.AM.html}{additions.AM}).
\end{project}

>>>>

Please define an Euclidean chain generator using this data structure, and prove its correctness (done  in ~\href{../theories/html/hydras.additions.AM.html}{additions.AM}, but with clumsy fresh proofs). The project is now to simplify the proofs. 
perhaps considering chains of type \texttt{code} as a refinement of functional chains. Please note that many proof scripts are copied verbatim from 
\texttt{Euclidean\_Chains} into \texttt{AM}.
\end{project}
